Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-19 manuscript/manuscript.tex
Add missing citations in manuscript
Add computation time section in manuscript

@@

We must also define a density function for the tesseroid model.
\citet{Sigismondi2012} measured a minimum and maximum density contrast for
the Neuqu\'en basin of -412kg/m$^3$ and -275kg/m$^3$, respectively.
We have chosen an exponential density variation (Eq.~\ref{eq:density-exp}) that assumes
the minimum value on the top surface and the maximum at 5014m depth (the thickest part
of the basin), with a value of $b$ equal to 3.
This density variation is in agreement with the ones used by
This density function can be seen on Fig.~\ref{fig:neuquen-basin-densities}.

>>>>

\section{Computation time comparison}

Because the density-based algorithm produces discretizations along the radial direction,
besides the latitudinal and longitudinal ones generated by the two dimensional adaptive
one, the computation time of the gravitational fields of variable density tesseroids
will be increased in comparison to the homogeneous density case.
In order to quantize this increase we perform a computation time comparison between the
homogeneous density case with the linear and the exponential ones.

We define a $20^\circ \times 20^\circ$ tesseroid of 1km of thickness and a single
computation point located at different heights (0m, 1km, 10km, 100km and 1000km) above
the top surface of the tesseroid.
Then we compute the gravitational potential $V$ and the $g_z$ that the tesseroid
generates on the computation point in case of an homogeneous density, a linear density
and an exponential density with $b = 3$ (Eq.~\ref{eq:density-exp}).
We perform 10000 computations for each field, density and computation height while
tracking the computation time for each one of them.
The final computation time is obtained as the mean value of these runs.

Fig.~\ref{fig:computation-times} shows the computation time ratio between the
computations times of the linear and exponential density with the one for an homogeneous
density, defined as:

\begin{equation}
    \text{Computation time ratio} = \frac{\Delta t}{\Delta t_\text{homog}},
\end{equation}

\noindent where $\Delta t_\text{homog}$ is the computation time for the homogeneous
density and $\Delta t$ is the computation time for the linear or the exponential
density.

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]{figures/computation-times.pdf}
}{
\includegraphics[width=0.5\linewidth]{figures/computation-times.pdf}
}
\caption{
    Computation times ratio between linear and exponential density tesseroids with an
    homogeneous one.
}
\label{fig:computation-times}
\end{figure}

@@

We must also define a density function for the tesseroid model.
\citet{Sigismondi2012} measured a minimum and maximum density contrast for
the Neuqu\'en basin of -412kg/m$^3$ and -275kg/m$^3$, respectively.
We have chosen an exponential density variation (Eq.~\ref{eq:density-exp}) that assumes
the minimum value on the top surface and the maximum at 5014m depth (the thickest part
of the basin), with a value of $b$ equal to 3.
This density variation is in the order of magnitude of the ones used by
\citet{Cowie1990} and \citet{Cordell1973}.
This density function can be seen on Fig.~\ref{fig:neuquen-basin-densities}.
